---
title: "Retrieve, enhance and align search results"
output: html_notebook
---

This process follows [the registration](https://osf.io/f5qdn) created after this meta-analysis was accepted in principle by the Journal of Business and Psychology.

# Packages used and set-up

```{r}
if(!require(pacman)) install.packages("pacman")
pacman::p_load(reticulate, tidyr, dplyr, jsonlite, purrr, stringr, rcrossref, bib2df, furrr,
               shiny, shinythemes, progress, progressr, keys, shinyjs, readr, synthesisr,
               rvest)

pacman::p_load_gh("gadenbuie/shinyThings")

#Enable progress updates
#handlers(global = TRUE) <- this needs to be run in the console for now
 handlers(handler_progress(
     format   = ":spin :current/:total (:message) [:bar] :percent in :elapsed (remaining: :eta)",
     width    = 60,
     complete = "=",
     clear = FALSE
   ))

 options(progressr.clear = FALSE)

 
#Adds progress bars to map and future_map functions
showing_progress <- function(x, fn, fn2, ..., steps = length(x)) {
  if(interactive() && !handlers(global = NA)) stop("To use this function, first run `handlers(global = TRUE)` in the console")
   p <- progressr::progressor(steps = steps)
   p(amount = 0)
   fn(x, function(...) {
     out <- fn2(...)
     p()
     out
   })
}


set.seed(1234)

#Import
source("API_keys.R")
source("crossref_and_related.R") #Functions to retrieve and edit citations
source("helpers.R") #Helper functions - sometimes simple wrappers to deal safely with NULLs

source_python("get_scrape_functions.py")

```

# Sources

- EBSCO host: OpenDissertations, Business Source Premier, PsycInfo - run search, then export to RIS
--> OpenDissertations: also save results to HTML to obtain links

- Google Scholar: scrape with serpapi, augment DOIs and abstracts with rcrossref
- SSRN: through Google Scholar, with site:ssrn.com (ssrn.org does not support Boolean operators), again augment with rcrossref
- Previous reviews: extract references with Grobid & citations with OpenCitations and Scopus
- Reference in included empirical articles: extract references with Grobid

## Import EBSCO

```{r import-ebsco, message=FALSE}

ebsco_psy_bs <- read_ref("search_results/EBSCO_psych_and_BS.ris")

ebsco_psy_bs <-  ebsco_psy_bs %>%
  mutate(doi = coalesce(doi, L3)) %>% 
  select(database, doi, author = author, title, year = Y1, type = source_type, abstract, journal, volume, issue, start_page, end_page, pubtitle = source) %>% 
  mutate(year = year %>% str_sub(1, 4) %>% as.numeric(),
         database = if_else(database == "buh", "BusinessSourcePremier", "PsycINFO"))

write_rds(ebsco_psy_bs, "results_aligned/ebsco_psy_bs.RDS")
```

## Import OpenDissertations

Here, links are essential but are not exported by EBSCOhost. Therefore, the following process was followed:

- Search on EBSCOhost and export RIS.
- Change Page Options to show 50 results per page
- Save page as HTML, then click through pages saving them all (ensure they are numbered so that they are read in the correct order)
- The helpers/ebsco-to-html folder includes a Google Chrome add-on that supports this process by scrolling down and saving the HTML files (so that the task consists of clicking next ~70 times)
- First read in RIS file, then add URLs.

```{r}

ebsco_open_diss <- read_ref("search_results/OpenDissertations.ris")

# HTML files
html_files <- list.files("./search_results/OpenDissertations_html/", 
                         pattern = "*.html", full.names = TRUE)

urls <- map(html_files, function(html_file) {
  html_file %>% read_html() %>% 
  html_elements(css='.display-info') %>% 
  html_element("a") %>% 
  html_attr("href")
}) %>% unlist()

ebsco_open_diss$resource_link <- urls

ebsco_open_diss <- ebsco_open_diss %>% 
  transmute(
    database = "OpenDissertations",
    title,
    author = author,
    year,
    abstract,
    type = source_type,
    resource_link
  )

write_rds(ebsco_open_diss, "results_aligned/ebsco_open_diss.RDS")
```

# Scrape Google Scholar with serpapi

*Given that Google Scholar will also be used to search SSRN, these hits are excluded here - and then used separately for SSRN*

```{r scrape-scholar}
scholar_results_1 <- get_scholar_results(
  q = '(diverse OR diversity OR heterogenous OR heterogeneity OR “team composition” OR “individual differences”) AND (team OR group) AND (performance OR creativity OR productivity OR innovation OR effectiveness) -site:ssrn.com', 
  max_results = 1000L, serp_key = serp_key, start = 0L) #Reduce max for testing - 1 search charged per 20 results

scholar_results_2 <- get_scholar_results(
  q = '((diversity AROUND(3)  performance) OR (diversity AROUND(3) creativity) OR (diversity AROUND(3) productivity) OR (diversity AROUND(3) innovation) OR (diversity AROUND(3) effectiveness)) AND (team OR group) -site:ssrn.com', 
  max_results = 1000L, serp_key = serp_key, start = 0L) 

scholar_results_3 <- get_scholar_results(
  q = '((“team composition” AROUND(3)  performance) OR (“team composition” AROUND(3) creativity) OR (“team composition” AROUND(3) productivity) OR (“team composition” AROUND(3) innovation) OR (“team composition” AROUND(3) effectiveness))', 
  max_results = 1000L, serp_key = serp_key, start = 0L) # Cannot exclude SSRN here due to search string length limitations


list_if_not <- function(x) {
  if (!is.list(x)) return(list(x))
  x
}

scholar_results <- bind_rows(
  scholar_results_1 %>% mutate(cite_string = "scholar_query_1", link = list_if_not(link)),
  scholar_results_2 %>% mutate(cite_string = "scholar_query_2", link = list_if_not(link)),
  scholar_results_3 %>% mutate(cite_string = "scholar_query_3", link = list_if_not(link))
)

write_rds(scholar_results, "search_results/scholar_results.RDS")
```

## Add crossref metadata

```{r}

#read_rds("search_results/scholar_results.RDS") -> scholar_results

scholar_results <- scholar_results %>% 
  unnest_wider(publication_info) %>% 
  select(-type) %>%
  unnest_wider(authors, names_sep = "_", names_repair = "universal") %>%
  unnest_wider(matches("authors_[0-9]+$"), names_sep = "_", names_repair = "unique") %>% #Unnests all columns matching the term
  mutate(year = str_extract(summary, "[0-9]{4}"),
         first_author = str_remove(summary, ",.*$") %>% 
           str_remove("-.*$") %>% str_remove("^[A-Z]* ")) %>%
  hoist(resources, resource_link = c(1, 3)) %>% 
  hoist(inline_links, citation_count = c("cited_by", "total"), citation_link = "serpapi_cite_link")

#Workaround for pmap as list columns cause problems - https://github.com/tidyverse/purrr/issues/846
ls_cols <- scholar_results %>% keep(is.list)
other_cols <- scholar_results %>% keep(~!(is.list(.x)))


# Augment with crossref data in background job
job::job(title = "Augment GS crossref", {
  handlers(global = TRUE) 
handlers(handler_progress(
  format   = ":spin :current/:total (:message) [:bar] :percent in :elapsed (remaining: :eta)",
  width    = 60,
  complete = "=",
  clear = FALSE
))
  plan(multisession, workers = 5) #Parallel API requests to crossref
  aug_df <- other_cols %>% showing_progress(function(...) future_pmap_dfr(..., .options = furrr_options(seed = TRUE)), function(...) {
    pacman::p_load(dplyr, stringr, tidyr, rcrossref)
    source("crossref_and_related.R") #Functions to retrieve and edit citations
    source("helpers.R") #Helper functions - sometimes simple wrappers to deal safely with NULLs
    df <- extract_crossref_try(tibble(...))
     # if ("doi" %in% names(df) && !is.na(df$doi)) df <- get_citation(df)
      df}, steps = nrow(.)) %>% 
    cbind(ls_cols)})

#Try to add abstracts from Scopus - tends to add some over crossref
aug_df$abstract[!is.na(aug_df$doi) & is.na(aug_df$abstract)] <- aug_df$doi[!is.na(aug_df$doi) & is.na(aug_df$abstract)] %>% na.omit() %>% 
  showing_progress(map_chr, function(x) {
 get_scopus_abstract(x) %>% {get_longer(.[[1]], .[[2]])}})

write_rds(aug_df, "results_aligned/scholar_augmented.RDS") 

```


## Search SSRN on Google Scholar

```{r}
ssrn_results_1 <- get_scholar_results(
  q = '(diverse OR diversity OR heterogenous OR heterogeneity OR “team composition” OR “individual differences”) AND (team OR group) AND (performance OR creativity OR productivity OR innovation OR effectiveness) site:ssrn.com', 
  max_results = 1000L, serp_key = serp_key, start = 0L) 

ssrn_results_2 <- get_scholar_results(
  q = '((diversity AROUND(3)  performance) OR (diversity AROUND(3) creativity) OR (diversity AROUND(3) productivity) OR (diversity AROUND(3) innovation) OR (diversity AROUND(3) effectiveness)) AND (team OR group) site:ssrn.com', 
  max_results = 1000L, serp_key = serp_key, start = 0L) 


ssrn_results <- bind_rows(
  ssrn_results_1 %>% mutate(cite_string = "ssrn_query_1"),
  ssrn_results_2 %>% mutate(cite_string = "ssrn_query_2")
)

write_rds(ssrn_results, "search_results/ssrn_results.RDS")
```

### Augment with crossref data

```{r}
#read_rds("search_results/ssrn_results.RDS") -> ssrn_results

ssrn_results <- ssrn_results %>% 
  unnest_wider(publication_info) %>% 
  select(-any_of("type")) %>%
  unnest_wider(authors, names_sep = "_", names_repair = "universal") %>%
  unnest_wider(matches("authors_[0-9]+$"), names_sep = "_", names_repair = "unique") %>% #Unnests all columns matching the term
  mutate(year = str_extract(summary, "[0-9]{4}"),
         first_author = str_remove(summary, ",.*$") %>% 
           str_remove("-.*$") %>% str_remove("^[A-Z]* ")) %>%
  hoist(resources, resource_link = c(1, 3)) %>% 
  hoist(inline_links, citation_count = c("cited_by", "total"), citation_link = "serpapi_cite_link")

#Workaround for pmap as list columns cause problems - https://github.com/tidyverse/purrr/issues/846
ls_cols_ssrn <- ssrn_results %>% keep(is.list)
other_cols_ssrn <- ssrn_results %>% keep(~!(is.list(.x)))

# Augment with crossref data in background job
job::job(title = "Augment SSRN crossref", {
  handlers(global = TRUE) 
handlers(handler_progress(
  format   = ":spin :current/:total (:message) [:bar] :percent in :elapsed (remaining: :eta)",
  width    = 60,
  complete = "=",
  clear = FALSE
))
  plan(multisession, workers = 5) #Parallel API requests to crossref
  aug_df_ssrn <- other_cols_ssrn %>% showing_progress(function(...) future_pmap_dfr(..., .options = furrr_options(seed = TRUE)), function(...) {
    pacman::p_load(dplyr, stringr, tidyr, rcrossref)
    source("crossref_and_related.R") #Functions to retrieve and edit citations
    source("helpers.R") #Helper functions - sometimes simple wrappers to deal safely with NULLs
    df <- extract_crossref(tibble(...))
     # if ("doi" %in% names(df) && !is.na(df$doi)) df <- get_citation(df)
      df}, steps = nrow(.)) %>% 
    cbind(ls_cols_ssrn)})

#Try to add abstracts from Scopus - tends to add some over crossref
aug_df_ssrn$abstract[!is.na(aug_df_ssrn$doi) & is.na(aug_df_ssrn$abstract)] <- 
  aug_df_ssrn$doi[!is.na(aug_df_ssrn$doi) & is.na(aug_df_ssrn$abstract)] %>% na.omit() %>% 
  showing_progress(map_chr, function(x) {
 get_scopus_abstract(x) %>% {get_longer(.[[1]], .[[2]])}})

write_rds(aug_df_ssrn, "results_aligned/ssrn_augmented.RDS") 
```

## Search and scrape NDLTD

This does not offer an API or a bulk export option - could harvest full dataset using [OAI-PMH](https://bepress.com/reference_guide_dc/digital-commons-oai-harvesting/) - possibly starting from this [Ruby script](https://github.com/astromechza/ndltd-scraper-ruby/blob/master/ndltd_downloader.rb), but web-scraping seems slightly more efficient.

High number of results due to apparently very liberal stemming - e.g. effectiveness to effective. Maybe repeat search after download?

```{r}
base_url <- "http://search.ndltd.org/search.php?q=%28diverse+OR+diversity+OR+heterogenous+OR+heterogeneity+OR+%22team+composition%22+OR+%22individual+differences%22%29+AND+%28team+OR+group%29+AND+%28performance+OR+creativity+OR+productivity+OR+innovation+OR+effectiveness%29&source_set_names=&year_start=&year_end="

total_results <- read_html(base_url) %>% html_elements("small") %>% 
  html_text() %>% str_subset("Showing 1 to 10") %>% 
  str_extract("[0-9]*(?= \\()") %>% as.numeric()

job::job(title = "Scrape NDLTD", {
  handlers(global = TRUE) 
handlers(handler_progress(
  format   = ":spin :current/:total (:message) [:bar] :percent in :elapsed (remaining: :eta)",
  width    = 60,
  complete = "=",
  clear = FALSE
))
  plan(multisession, workers = 2) #Parallel API requests to crossref
  ndltd_results <- showing_progress(seq.int(0, total_results, by = 10), future_map, function(start) {
    pacman::p_load(dplyr, rvest, stringr, purrr)
    page <- read_html(paste0(base_url, "&start=", start))
    results <- page %>% html_elements(".search_table_detail_col")
  
    titles <- map_chr(results, ~html_element(.x, "h4") %>% html_text())
    links <- paste0("http://search.ndltd.org/", 
                    map_chr(results, ~html_element(.x, "h4") %>% html_element("a") %>% html_attr("href")))
    
    author_years <- map(results, ~html_elements(.x, "em") %>% html_text()) %>% transpose()
    
    abstracts <- page %>% html_elements(".record_description") %>% html_text()
    
    tibble::tibble(database = "NDLTD", title = titles,
           author = author_years[[1]] %>% unlist(),
           year = author_years[[2]] %>% unlist() %>% str_extract("[0-9]{4}"),
           abstract = abstracts,
           type = "thesis_dissertation",
           resource_link = links)
  })
})


ndltd_results_df <- ndltd_results %>% bind_rows() %>% 
  mutate(across(where(is.character), str_trim))
```

### Sort out abstract languages

Identify abstract language, then extract English abstract if available, and otherwise translate first 500 characters

```{r}
pacman::p_load_gh("ropensci/cld2")

collapse_short_strings <- function(x, cut_off = 500) {
  if (sum(str_length(x)) < cut_off) return(x) 
  merge <- str_length(x) < cut_off
  if (all(!merge)) return(x)
  now <- which(merge)[1]
  y <- x
  if(now == length(x)) {
    y[length(x) - 1] <- paste(x[length(x) - c(1,0)], collapse = " \\ ")
    y <- y[-length(x)]
  } else if (now == 1) {
    y[now+1] <- paste(x[now + c(0, 1)], collapse = " \\ ")
    y <- y[-now]
  }
  
  else {
    direction <- if_else(str_length(y[now+1])>str_length(y[now-1]), -1, 1)
    y[now + direction] <- paste(x[sort(now + c(0, direction))], collapse = " \\ ")
    y <- y[-now]
  }
  collapse_short_strings(y, cut_off = cut_off)
}


abstract_language <- function(abstracts) {
  map(abstracts, function(x) {
  
 res <- cld2::detect_language_mixed(x)
 language <- res$classification$code[res$classification$proportion == max(res$classification$proportion)][1]
 translate <- TRUE
 if ("en" %in% res$classification$code && 
     # When English is either a substantial chunk, or the most frequent language
     (res$classification$proportion[res$classification$code == "en"] * res$bytes > 1000 ||
     res$classification$proportion[res$classification$code == "en"] == max(res$classification$proportion))) {
   translate <- FALSE
 } 
 
 english_abstract <- x
 
 if (language != "en") {
   if (str_detect(x, " / ")) {
     segments <- str_split_1(x, " / ")
     segments <- collapse_short_strings(segments)
     segments <- segments[cld2::detect_language(segments) %>% {is.na(.) | . == "en"}]
     if(length(segments) > 0) english_abstract <- paste(segments, collapse = " / ")
   }
 }
 

 tibble(language = language, translate = translate, english_abstract = english_abstract)
  }) %>% bind_rows()
}

pacman::p_load(googleLanguageR)
gl_auth("google_translate.json")
translate <- function(x, drop_tags = TRUE) {
  if (sum(str_length(x)) > 5000) {
    if(usethis::ui_nope(glue::glue("Translation of more than {sum(str_length(x))} characters requested. Continue?"))) return(NULL)
  }
  if (drop_tags) {
    x <- str_replace_all(x, "<.*?>", " ")
  }
  which_NA <- is.na(x)
  x <- c(na.omit(x))
  t <- gl_translate(x)
  t %>%
    count(detectedSourceLanguage) %>%
    transmute(N = paste0(detectedSourceLanguage, ": ", n)) %>%
    pull() %>%
    glue::glue_collapse(sep = ", ", last = "&") %>%
    message("Detected languages: ", .)
  out <- character(length(which_NA))
  out[!which_NA] <- t %>% pull(translatedText)
  out[which_NA] <- NA
  out
}

ndltd_results_df <- ndltd_results_df %>% mutate(abstract_language(abstract))

translate_abstract_if <- function(abstract, translate, n_char = 500) {
  res <- abstract
  res[translate] <- paste(translate(str_sub(abstract[translate], 1, n_char)), str_sub(abstract[translate], n_char + 1))
  res
}

ndltd_results_df <- ndltd_results_df %>% 
  mutate(translate = if_else(str_length(abstract) < 100, FALSE, translate), # Fewer 100 char indicates that abstract is missing
         translate_narrow = if_else(cld2::detect_language(english_abstract) %>% {!is.na(.) & . == "en"}, FALSE, translate)) %>%
  mutate(english_abstract = translate_abstract_if(english_abstract, translate_narrow, 500))

ndltd_results_df %>% write_rds("search_results/ndltd_results.RDS")

ndltd_results_df <- read_rds("search_results/ndltd_results.RDS")

ndltd_results_df %>% bind_rows() %>% write_rds("results_aligned/ndltd_results.RDS")

```


## Query Scopus for references in previous reviews

Remember: need to be in university network / VPN to access Scopus API

```{r}
previous <- c(
  bell_2011 = "10.1177/0149206310365001",
  bowers_2000 = "10.1177/104649640003100303",
  bui_2019 = "10.1111/apps.12203",
  horwitz_2007 = "10.1177/0149206307308587",
  huelsheger_2009 = "10.1037/a0015978",
  # joshi_2009 = , no DOI, but have PDF
  peeters_2006 = "10.1002/per.588",
  stahl_2010 = "10.1057/jibs.2009.85",
  van_dijk_2012 = "10.1016/j.obhdp.2012.06.003",
  webber_2001 = "10.1016/S0149-2063(00)00093-3",
  wei_2015 = "10.3724/SP.J.1041.2015.01172",
  bunderson_2018 = "10.1146/annurev-orgpsych-032117-104500",
  sulik_2021 = "10.1177/17456916211006070",
  # williams_1998 = , - PDF without OCR, so maybe needs to be done manually
  yadav_2020 = "10.1108/EDI-07-2019-0197"
)

#Beware: this function cannot cache results - so don't call repeatedly with same dois.
#Sometimes returns inconsistent types - so cannot use map_dfr directly
scopus_refs <- previous %>% showing_progress(map, get_scopus_references)

scopus_refs_df <- bind_rows_to_list(!!! scopus_refs, .id = "cited_in")

scopus_refs_df <- scopus_refs_df %>% 
  mutate(across(where(is.list), unlist_w_NULLs)) %>% 
  transmute(
    database = "previous_reviews",
    cited_in,
    doi,
    scopus_id = id,
    title,
    author = authors,
    volume,
    issue,
    year = str_sub(coverDate, 1, 4) %>% na_if("NULL"),
    start_page = first,
    end_page = last,
    pubtitle = sourcetitle,
    pubtype = if_else(str_detect(pubtitle, fixed("journal", ignore_case=TRUE)), "journal-article", NA_character_),
    citation_count = citedbycount,
    in_scopus = type == "resolvedReference"
  )

# Add abstracts

## Cannot easily be parralelised (reticulate and future are not compatible),
## but Scopus API is fast
scopus_refs_df$abstract[!is.na(scopus_refs_df$doi)] <- scopus_refs_df$doi %>% na.omit() %>% 
  showing_progress(map_chr, function(x) {
 get_scopus_abstract(x) %>% {get_longer(.[[1]], .[[2]])}})

## Try scopus id for hits listed in scopus (not just resolved from PDF), but without DOI
scopus_refs_df$abstract[is.na(scopus_refs_df$doi) & scopus_refs_df$in_scopus] <- 
  scopus_refs_df$scopus_id[is.na(scopus_refs_df$doi) & scopus_refs_df$in_scopus]  %>% 
  showing_progress(map_chr, function(x) {
 get_scopus_abstract(x, id_type = "scopus_id") %>% {get_longer(.[[1]], .[[2]])}})

## Try crossref for remaining DOIs
scopus_refs_df$abstract[!is.na(scopus_refs_df$doi) & is.na(scopus_refs_df$abstract)] <- 
  scopus_refs_df$doi[!is.na(scopus_refs_df$doi) & is.na(scopus_refs_df$abstract)] %>% 
  showing_progress(map, possibly(cr_abstract, ""))


write_rds(scopus_refs_df, "results_aligned/scopus_previous.RDS")


```

## Extract citations from PDFs directly

The above only works for sources indexed in Scopus. For others, GROBID is used to extract references from PDFs - usually, this should be done with a local installation, but that is currently difficult on Macs with M2 and without a Crossref subscription - so we use the web service which appears acceptable for the kind of load expected here. (https://github.com/kermitt2/grobid_client_python/issues/54#issuecomment-1272509755). This makes it rather slow ... approx. 1 min per PDF.

Note that this does not recognise text in PDF scans - these need to be OCR-ed before.

```{r}
pacman::p_load(sys)

fs <- list.files("./past_review_PDFs", pattern = ".pdf", full.names = TRUE)

# OCR them (this also compresses the ones already containing text, if that takes 
# too long, could also first try GROBID and only OCR failures
showing_progress(fs, walk, \(x) normalizePath(x) %>% {system(glue::glue('ocrmypdf --skip-text "{.}" "{.}"'))})

#OCR the Chinese doc again with eng + chi_sim
system(glue::glue("ocrmypdf -l eng+chi_sim --redo-ocr '{fs[2]}' '{fs[2]}'"))


# Request from GROBID
refs <- showing_progress(fs, map, \(f) {
  f_bib <- paste0(tools::file_path_sans_ext(f), ".bib")
  if (!file.exists(f_bib)) {
    bib <- parse_pdf_refs(f)
    writeLines(bib, f_bib)
  } else {
    message("Skipping retrieval for ", basename(f), ". Instead, reading references from .bib file")
    bib <- read_lines(f_bib)
  }
  if (length(bib) == 0 || (length(bib) == 1 && bib[1] == "")) {
    message("No references found for ", f)
    return(data.frame())
  }
  
  res <- bib2df::bib2df(f_bib) %>% 
    collapse_to_string(where(is.list)) 
  res$database <- paste0("references_", basename(f))
  res
}) %>% set_names(fs)

refs <- bind_rows(refs) %>% rename_with(tolower)

refs$abstract <- NA

refs$abstract[!is.na(refs$doi)] <- refs$doi %>% na.omit() %>% 
  showing_progress(map_chr, function(x) {
 get_scopus_abstract(x) %>% {get_longer(.[[1]], .[[2]])}})

pdf_refs <- refs %>% 
  mutate(pages = str_replace(pages, "--", "-")) %>% 
  transmute(
    database,
    doi,
    title,
    author = author,
    volume,
    issue = number,
    year,
    start_page = str_extract(pages, ".*(?=\\-)"),
    end_page = str_extract(pages, "(?<=\\-{1,2})\\d+"),
    journal = journal,
    pubtitle = booktitle,
    pubtype = type,
    publisher = publisher,
    abstract = abstract
  ) 

saveRDS(pdf_refs, "results_aligned/grobid_refs.RDS")
```

### Repeat for included articles

## Query citations of meta-analyses (forward chasing)

Combine Scopus and OpenCitations - in spite of claims that latter has [similar coverage](https://opencitations.wordpress.com/2021/10/27/coverage-of-open-citation-data-approaches-parity-with-web-of-science-and-scopus/), on some test items there were ~33% more Scopus citations. Google Scholar would be more comprehensive - but much harder to deduplicate without DOIs and with fragmentary abstracts.

Note that the Scopus API access to citations is disabled by default - it needs to be enabled by their customer support on a case-by-case basis.

```{r}
pacman::p_load(citecorp)

previous_metas <- c(
  bell_2011 = "10.1177/0149206310365001",
  bowers_2000 = "10.1177/104649640003100303",
  bui_2019 = "10.1111/apps.12203",
  horwitz_2007 = "10.1177/0149206307308587",
  huelsheger_2009 = "10.1037/a0015978",
  joshi_2009 = "10.5465/amj.2009.41331491",
  peeters_2006 = "10.1002/per.588",
  stahl_2010 = "10.1057/jibs.2009.85",
  van_dijk_2012 = "10.1016/j.obhdp.2012.06.003",
  webber_2001 = "10.1016/S0149-2063(00)00093-3",
  wei_2015 = "10.3724/SP.J.1041.2015.01172"
)

  plan(multisession, workers = 5) #Parallel API requests to crossref

open_citations <- oc_coci_cites(previous_metas) %>% split(.$cited) 

# Request citations in batches - otherwise fails with "header to large" request
open_citations_aug <- open_citations %>% 
  showing_progress(function(...) future_map_dfr(..., .id = "cited", .options = furrr_options(seed = TRUE)), function(df) {
    tryCatch({
      step_size <- 100
      map(seq(1, nrow(df), step_size), function(i) {
        df$citing[i:min(nrow(df), i+step_size-1)] %>% oc_coci_meta()
      }) %>% bind_rows()
    }, error = function(cond) {
      message("Error occured for ", df$cited[1])
      message("Original message was: ")
      message(cond)
      return(data.frame())
    })
    })

open_citations_aug$abstract <- open_citations_aug$doi %>% showing_progress(map_chr, function(x) {
 get_scopus_abstract(x) %>% {get_longer(.[[1]], .[[2]])}})

open_citations_aug <- open_citations_aug %>%
  transmute(database = "OpenCitations_previous",
            cited_in = cited,
         doi = doi,
         author = author,
         year = year,
         title = title,
         abstract = abstract,
         start_page = str_extract(page, ".*(?=\\-)"),
         end_page = str_extract(page, "(?<=\\-{1,2})\\d+"),
         pubtitle = source_title,
         resource_link = oa_link,
         citation_count = citation_count,
         issue,
         volume
         ) %>% tibble()

write_rds(open_citations_aug, "results_aligned/open_citations_df.RDS")
```


```{r}
scopus_citations <- showing_progress(previous_metas, map, get_scopus_citing_works) %>%
  set_names(previous_metas) %>% 
  map2(names(.), ~.x %>% mutate(across(where(is.list), unlist_w_NULLs), cited_in = .y)) %>%
  bind_rows()

# Not scraping abstracts here since they will largely overlap with OpenCitations
# scopus_citations$abstract[!is.na(scopus_citations$doi)] <- scopus_citations$doi[!is.na(scopus_citations$doi)] %>% showing_progress(map_chr, function(x) {
#  get_scopus_abstract(x) %>% {get_longer(.[[1]], .[[2]])}})

scopus_citations <- scopus_citations %>%
  transmute(database = "ScopusCitations_previous",
            cited_in,
            scopus_id = eid,
         doi = doi,
         author = author_names,
         year = coverDate %>% str_sub(1, 4) %>% as.numeric(),
         title = title,
         abstract = NA_character_,
         pubtype = subtypeDescription,
         pubtitle = publicationName,
         volume,
         issue = issueIdentifier,
         start_page = str_extract(pageRange, ".*(?=\\-)"),
         end_page = str_extract(pageRange, "(?<=\\-{1,2})\\d+"),
         citation_count = citedby_count,
         oa_type = freetoreadLabel
         ) %>% tibble()

write_rds(scopus_citations, "results_aligned/scopus_citations_df.RDS")
```

